Mixture Models for Single-Cell Assays with Application to Vaccine Studies: Supplementary Materials

### 2013-05-17 MIMOSA.tex
Update S4

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics{TIKZFig3.eps}
%   \begin{tikzpicture} [auto, node distance=0cm]
%   \node at (0,0) (A) {
%\begin{tikzpicture}
%    \node [anchor=south west] at (0,0) (foo) {\includegraphics[width=0.45\columnwidth]{Figures/Sim_Onesided_ROC_5000.pdf}};
%    \begin{scope}[x={(foo.south east)},y={(foo.north west)}]
%        \node at (0,1) [font=\small\sffamily] {A} ;
%        \end{scope}
%    \end{tikzpicture}
%    };
%    \node [right=of A] (B) {
%    \begin{tikzpicture}
%    \node [anchor=south west] at (0,0) (bar) {\includegraphics[width=0.45\columnwidth]{Figures/Sim_Onesided_FDR_5000.pdf}};
%    \begin{scope}[x={(bar.south east)},y={(bar.north west)}]
%    \node at (0,1) [font=\small\sffamily] {B} ;
%    \end{scope}
%    \end{tikzpicture}
%    };
%        \node [below=of A] (C) {
%    \begin{tikzpicture}
%    \node [anchor=south west] at (0,0) (c) {\includegraphics[width=0.45\columnwidth]{Figures/Sim_Twosided_ROC_5000.pdf}};
%    \begin{scope}[x={(c.south east)},y={(c.north west)}]
%    \node at (0,1) [font=\small\sffamily] {C} ;
%    \end{scope}
%    \end{tikzpicture}
%    };
%    \node [right=of C] (D) {
%    \begin{tikzpicture}
%    \node [anchor=south west] at (0,0) (d) {\includegraphics[width=0.45\columnwidth]{Figures/Sim_Twosided_FDR_5000.pdf}};
%    \begin{scope}[x={(d.south east)},y={(d.north west)}]
%    \node at (0,1) [font=\small\sffamily] {D} ;
%    \end{scope}
%    \end{tikzpicture}
%    };
%
%\end{tikzpicture}
   \caption{Comparison of positivity detection methods on data simulated from the one-sided and two--sided models. Ten simulations were generated at an $N$ of 50,000 total counts using hyper-parameter estimates from real ICS data (IFN-$\gamma$ expressing CD4+ T-cells stimulated with ENV-1-PTEG from HVTN065) with a five-fold effect size between responder and non-responder components. A) Average ROC curve over the 10 simulated data sets (N=50,000), one--sided B) Average observed and nominal false discovery rate over 10 simulated data sets (N=50,000), one--sided. C) Average ROC curves, two--sided model. D) Average observed and nominal FDR, two--sided model. Curves are shown for MIMOSA, Fisher's exact test, the likelihood ratio test, and log fold-change. Results for MIMOSA fit to a model violating model assumptions, as well as other values of N and I (number of subjects) are in Supplementary Figure 3. This figure appears in color in the electronic version of this article.}\label{fig:simulations}
\end{figure}

>>>>

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics{TIKZFig3.eps}
%   \begin{tikzpicture} [auto, node distance=0cm]
%   \node at (0,0) (A) {
%\begin{tikzpicture}
%    \node [anchor=south west] at (0,0) (foo) {\includegraphics[width=0.45\columnwidth]{Figures/Sim_Onesided_ROC_5000.pdf}};
%    \begin{scope}[x={(foo.south east)},y={(foo.north west)}]
%        \node at (0,1) [font=\small\sffamily] {A} ;
%        \end{scope}
%    \end{tikzpicture}
%    };
%    \node [right=of A] (B) {
%    \begin{tikzpicture}
%    \node [anchor=south west] at (0,0) (bar) {\includegraphics[width=0.45\columnwidth]{Figures/Sim_Onesided_FDR_5000.pdf}};
%    \begin{scope}[x={(bar.south east)},y={(bar.north west)}]
%    \node at (0,1) [font=\small\sffamily] {B} ;
%    \end{scope}
%    \end{tikzpicture}
%    };
%        \node [below=of A] (C) {
%    \begin{tikzpicture}
%    \node [anchor=south west] at (0,0) (c) {\includegraphics[width=0.45\columnwidth]{Figures/Sim_Twosided_ROC_5000.pdf}};
%    \begin{scope}[x={(c.south east)},y={(c.north west)}]
%    \node at (0,1) [font=\small\sffamily] {C} ;
%    \end{scope}
%    \end{tikzpicture}
%    };
%    \node [right=of C] (D) {
%    \begin{tikzpicture}
%    \node [anchor=south west] at (0,0) (d) {\includegraphics[width=0.45\columnwidth]{Figures/Sim_Twosided_FDR_5000.pdf}};
%    \begin{scope}[x={(d.south east)},y={(d.north west)}]
%    \node at (0,1) [font=\small\sffamily] {D} ;
%    \end{scope}
%    \end{tikzpicture}
%    };
%
%\end{tikzpicture}
   \caption{Comparison of positivity detection methods on data simulated from the one-sided and two--sided models. Ten simulations were generated at an $N$ of 50,000 total counts using hyper-parameter estimates from real ICS data (IFN-$\gamma$ expressing CD4+ T-cells stimulated with ENV-1-PTEG from HVTN065) with a five-fold effect size between responder and non-responder components. A) Average ROC curve over the 10 simulated data sets (N=50,000), one--sided B) Average observed and nominal false discovery rate over 10 simulated data sets (N=50,000), one--sided. C) Average ROC curves, two--sided model. D) Average observed and nominal FDR, two--sided model. Curves are shown for MIMOSA, Fisher's exact test, the likelihood ratio test, and log fold-change. Results for MIMOSA fit to a model violating model assumptions, as well as other values of N are in Supplementary Figure 3, and for varying values of I (number of observations) are in Supplementary Figure 4. This figure appears in color in the electronic version of this article.}\label{fig:simulations}
\end{figure}

### 2013-05-17 SupplementaryMaterialMIMOSA.tex
Update S4

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
\begin{tikzpicture} [auto,node distance=0cm]
%\node at (0,0) (A) {
%\begin{tikzpicture}
%    \node[anchor=south west,inner sep=0] at (0,0) (a) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_5000.pdf}};
%    \begin{scope} [x={(a.south east)},y={(a.north west)}]
%        \node at (0,1) [font=\small\sffamily] {A} ;
%    \end{scope}
%    \end{tikzpicture}
%    };
%    \node [right=of A] (B) {
%    \begin{tikzpicture}
%    \node[anchor=south west, inner sep=0] at (0,0) (b) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_5000.pdf}};
%        \begin{scope} [x={(b.south east)},y={(b.north west)}]
%        \node at (0,1) [font=\small\sffamily] {B} ;
%        \end{scope}
%    \end{tikzpicture}
%    };
    \node at (0,0) (A) {
    \begin{tikzpicture}
     \node[anchor=south west,inner sep=0] at (0,0) (c) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_50K.pdf}};
         \begin{scope} [x={(c.south east)},y={(c.north west)}]
                 \node at (0,1) [font=\tiny\sffamily] {A} ;
	\end{scope}
     \end{tikzpicture}
     };
     \node [right=of A] (B) {
     \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (d) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_50K.pdf}};
        \begin{scope} [x={(d.south east)},y={(d.north west)}]
            \node at (0,1) [font=\tiny\sffamily] {B} ;
\end{scope}
    \end{tikzpicture}
    };
  \node [below=of A] (C) {
\begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) (e) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_10K.pdf}};
    \begin{scope} [x={(e.south east)},y={(e.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {C} ;
    \end{scope}
    \end{tikzpicture}
    };
    \node [right=of C] (D) {
    \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (f) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_10K.pdf}};
        \begin{scope} [x={(f.south east)},y={(f.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {D} ;
        \end{scope}
    \end{tikzpicture}
    };
%     \node [below=of C] (E) {
%     \begin{tikzpicture}
%      \node[anchor=south west,inner sep=0] at (0,0) (g) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_1000.pdf}};
%          \begin{scope} [x={(g.south east)},y={(g.north west)}]
%                  \node at (0,1) [font=\tiny\sffamily] {E} ;
% 	\end{scope}
%      \end{tikzpicture}
%      };
%      \node [right=of E] (F) {
%      \begin{tikzpicture}
%     \node[anchor=south west, inner sep=0] at (0,0) (h) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_1000.pdf}};
%         \begin{scope} [x={(h.south east)},y={(h.north west)}]
%             \node at (0,1) [font=\tiny\sffamily] {F} ;
% \end{scope}
%     \end{tikzpicture}
%     };
 \end{tikzpicture}
   \caption{Unconstrained MIMOSA model fit to data from a model
     violating model assumptions and to two-sided data with small
     counts. Data was simulated from a model where proportions were
     sampled from a truncated normal distribution over $[0,1]$ rather
     than a Beta distribution.  A) The average ROC from 10 simulation
     with N=5,000 events. B) The average observed and nominal FDR from
     10 simulations with N=5,000 events. C) Average ROC for N=1,000
     events D) Average observed and nominal FDR for N=1,000 events.
% MIMOSA fit to two-sided data were simulated from the standard model
% with N=1,000 events. E) Average ROC curves from 10 simulations and
% F) average observed vs nominal FDR from 10 simulations. This figure
% appears in color in the electronic version of this article.
}
   \label{webfig:simulations_trunc}
\end{figure}
\clearpage

>>>>

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
\begin{tikzpicture} [auto,node distance=0cm]
%\node at (0,0) (A) {
%\begin{tikzpicture}
%    \node[anchor=south west,inner sep=0] at (0,0) (a) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_5000.pdf}};
%    \begin{scope} [x={(a.south east)},y={(a.north west)}]
%        \node at (0,1) [font=\small\sffamily] {A} ;
%    \end{scope}
%    \end{tikzpicture}
%    };
%    \node [right=of A] (B) {
%    \begin{tikzpicture}
%    \node[anchor=south west, inner sep=0] at (0,0) (b) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_5000.pdf}};
%        \begin{scope} [x={(b.south east)},y={(b.north west)}]
%        \node at (0,1) [font=\small\sffamily] {B} ;
%        \end{scope}
%    \end{tikzpicture}
%    };
    \node at (0,0) (A) {
    \begin{tikzpicture}
     \node[anchor=south west,inner sep=0] at (0,0) (c) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_50K.pdf}};
         \begin{scope} [x={(c.south east)},y={(c.north west)}]
                 \node at (0,1) [font=\tiny\sffamily] {A} ;
	\end{scope}
     \end{tikzpicture}
     };
     \node [right=of A] (B) {
     \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (d) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_50K.pdf}};
        \begin{scope} [x={(d.south east)},y={(d.north west)}]
            \node at (0,1) [font=\tiny\sffamily] {B} ;
\end{scope}
    \end{tikzpicture}
    };
  \node [below=of A] (C) {
\begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) (e) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_10K.pdf}};
    \begin{scope} [x={(e.south east)},y={(e.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {C} ;
    \end{scope}
    \end{tikzpicture}
    };
    \node [right=of C] (D) {
    \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (f) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_10K.pdf}};
        \begin{scope} [x={(f.south east)},y={(f.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {D} ;
        \end{scope}
    \end{tikzpicture}
    };
%     \node [below=of C] (E) {
%     \begin{tikzpicture}
%      \node[anchor=south west,inner sep=0] at (0,0) (g) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_1000.pdf}};
%          \begin{scope} [x={(g.south east)},y={(g.north west)}]
%                  \node at (0,1) [font=\tiny\sffamily] {E} ;
% 	\end{scope}
%      \end{tikzpicture}
%      };
%      \node [right=of E] (F) {
%      \begin{tikzpicture}
%     \node[anchor=south west, inner sep=0] at (0,0) (h) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_1000.pdf}};
%         \begin{scope} [x={(h.south east)},y={(h.north west)}]
%             \node at (0,1) [font=\tiny\sffamily] {F} ;
% \end{scope}
%     \end{tikzpicture}
%     };
 \end{tikzpicture}
   \caption{Unconstrained MIMOSA model fit to data from a model
     violating model assumptions and to two-sided data with small
     counts. Data was simulated from a model where proportions were
     sampled from a truncated normal distribution over $[0,1]$ rather
     than a Beta distribution.  A) The average ROC from 10 simulation
     with N=50,000 events. B) The average observed and nominal FDR from
     10 simulations with N=50,000 events. C) Average ROC for N=10,000
     events D) Average observed and nominal FDR for N=10,000 events.
}
   \label{webfig:simulations_trunc}
\end{figure}
\clearpage

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
\begin{tikzpicture} [auto,node distance=0cm]
    \node at (0,0) (A) {
    \begin{tikzpicture}
     \node[anchor=south west,inner sep=0] at (0,0) (c) {\includegraphics[width=0.75	\columnwidth]{Figures/Sim_OneSided_ROC_varyNobs.pdf}};
         \begin{scope} [x={(c.south east)},y={(c.north west)}]
                 \node at (0,1) [font=\tiny\sffamily] {A} ;
	\end{scope}
     \end{tikzpicture}
     };
     \node [below=of A] (B) {
     \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (d) {\includegraphics[width=0.75\columnwidth]{Figures/Sim_OneSided_FDR_varyNobs.pdf}};
        \begin{scope} [x={(d.south east)},y={(d.north west)}]
            \node at (0,1) [font=\tiny\sffamily] {B} ;
\end{scope}
    \end{tikzpicture}
    };
  \end{tikzpicture}
   \caption{One--sided MIMOSA model fit to simulated data with 50K events and varying values of I (number of observations). A) Average ROC curves from 10 simulations for 20, 50 and 100 observations. B) Average observed and nominal FDR from 10 simulations for 20, 50, and 100 observations. This figure appears in color in the electronic version of this article.
}
   \label{webfig:simulations_Nobs}
\end{figure}
\clearpage
